---
title: "Analysis"
author: "David John Baker"
date: "09/06/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Introduction

This document provides the analysis for "Lyrics’ Emotional Influences in Songs: A Conceptual Replication of Ali and Peynircioğlu’s (2006) Study".
The script creates both figures for the paper as well as the statistical analysis. 

## Software Import 

```{r}
library(ggridges)
library(ez)
library(multcomp)
library(lme4)
library(sjPlot)
library(patchwork)
library(tidyverse)


df_complete <- read_csv("Complete_Data.csv", col_types = cols(age = col_character()))

df_complete <- df_complete %>%
  mutate(age = str_replace_all(string = age, pattern = "eighteen", replacement = "18")) %>%
  mutate(age = str_replace_all(string = age, pattern = "3", replacement = NA_character_)) %>%
  mutate(age = as.numeric(age))
```

## EDA Viz

Create reference columns for ggplot subsetting.

```{r}
# Plot of 4x2 ANOVA
valence_table <- tribble(
  ~valence, ~response,
  "Positive", "Happy",
  "Positive", "Calm",
  "Negative", "AngryStressful",
  "Negative", "Sad"
)

valence_table_exact <- read_csv("data/valence_sheet.csv")


df_complete %>% 
  left_join(valence_table_exact) -> df_complete
```



```{r}

# Standard Deviation of Mean Function
std <- function(x) sd(x)/sqrt(length(x))

# Make Mean Rating Per Condition 
(df_complete %>%
  dplyr::select(subject, Happy:AngryStressful, Condition, Valence) %>%
  pivot_longer(cols = Happy:AngryStressful, names_to = "response",values_to = "rating") %>%
  # Congrency Add Here!!
  mutate(congru = Valence == response) %>%
  filter(congru == TRUE) %>%
  group_by(Condition, response) %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating),
            max_rating = max(rating),
            min_rating = min(rating),
            se_rating = std(rating),
            number_of_ratings = n()) %>%
  left_join(valence_table) %>%
  mutate(response = factor(response, levels = c("Happy","Calm","AngryStressful","Sad"))) %>%
  ggplot(aes(x = response, y = mean_rating, fill = valence)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Condition) +
  geom_errorbar(aes(ymin = mean_rating + se_rating, ymax = mean_rating - se_rating)) + 
  labs(title = "Mean Ratings Per Congruant Condition",
       caption = "Error Bars represent Standard Error of Mean",
       x = "Response Category",
       y = "Mean Rating") +
  theme_minimal() -> factorial_plot)

# Alternate Visualization of Above Data 
df_complete %>%
  dplyr::select(subject, Happy:AngryStressful, Condition, Valence) %>%
  pivot_longer(cols = Happy:AngryStressful, names_to = "response",values_to = "rating") %>%
  # Congrency Add Here!!
  mutate(congru = Valence == response) %>%
  filter(congru == TRUE) %>%
  group_by(Condition, response) %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating),
            max_rating = max(rating),
            min_rating = min(rating),
            se_rating = std(rating),
            number_of_ratings = n()) %>%
  ggplot(aes(x = response, y = mean_rating, color = Condition)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymin = mean_rating + se_rating, ymax = mean_rating - se_rating)) + 
  labs(title = "Mean Rating Per Condition",
       subtitle = "Error Bars are Standard Error of Mean",
       x = "Response Category",
       y = "Mean Rating") +
  theme_minimal()
```

### Data Distributions

Exploring distributions of other variables in dataset. 

```{r}
df_complete %>%
  dplyr::select(subject, Happy:AngryStressful, Condition, title) %>%
  pivot_longer(cols = Happy:AngryStressful, names_to = "response",values_to = "rating") %>%
  ggplot(aes(x = rating, y = title)) +
  geom_density_ridges() +
  facet_wrap(~response) + 
  labs(title = "Distributions of Emotion Ratings",
       x = "Rating Density",
       y = "Stimuli") +
  theme_minimal()


df_complete %>%
  dplyr::select(Familiar, title, Valence) %>%
  ggplot(aes(x = Familiar, y = title, fill = Valence)) +
  geom_density_ridges() +
  labs(title = "Distributions of Familiar Ratings",
       subtitle = "Most Participants are Not familiar with stimuli",
       x = "Rating Density",
       y = "Stimuli") +
  theme_minimal()
```

## Replication of Pre-Registered Analysis

Below Analysis Includes

* [X] 4x2 ANOVA 
* [X] Interaction Effects
* [X] Main Effects of Lyrics and Emotion 
* [ ] Planned Contrast of Lyrics Making Positive Worse, Negative Better 
* [X] Correlate GMSI General with Emotional Ratings
* [X] Correalte GMSI Emotional with Emotional Ratings

```{r}
long_df_complete <- df_complete %>%
  dplyr::select(subject, Happy:AngryStressful, Condition, title, Valence) %>%
  pivot_longer(cols = Happy:AngryStressful, names_to = "response",values_to = "rating") %>%
  # Congrency Filter 
  mutate(congru = Valence == response) %>%
  filter(congru == TRUE)

factorial_anova <- ezANOVA(
  data = long_df_complete
  , dv = .(rating)
  , wid = .(subject)
  , within = .(Condition, response),
  type = 3, # Do you want to do Type III sum of Squares, doesnt change results...
  detailed = TRUE,
  return_aov = TRUE
)

# Check Exlusion Criteria from Pre-Registration since this is on border
print(factorial_anova)
```


Analysis here shows significant omnibus test, main effect of condition as well as emotion.
Interaction needs to be clarified. 

## Within Linear Model Framework 

```{r}

anova_model <- lmer(rating ~ Condition*response + (1|subject), data = long_df_complete)
anova(anova_model)

# All Pairwise post-hoc are significant EXCEPT Sad-- Calm
summary(glht(anova_model, linfct =mcp(response= "Tukey"),test = adjusted(type = "bonferroni")))

# Main Effect of condition significant 
summary(glht(anova_model, linfct =mcp(Condition= "Tukey"), test = adjusted(type = "bonferroni")))


(long_df_complete %>%
  group_by(response) %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating),
            max_rating = max(rating),
            min_rating = min(rating),
            se_rating = std(rating),
            number_of_ratings = n()) %>%
  left_join(valence_table) %>%
  mutate(response = factor(response, levels = c("Happy","Calm","AngryStressful","Sad"))) %>%
  ggplot(aes(x = response, y = mean_rating, fill = valence)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_rating + se_rating, ymax = mean_rating - se_rating)) + 
  labs(title = "Mean Rating Per Condition",
       subtitle = "Error Bars are Standard Error of Mean",
       x = "Response Category",
       y = "Mean Rating") +
  theme_minimal() -> factorial_plot_main_effect_emotion)

(long_df_complete %>%
  group_by(Condition) %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating),
            max_rating = max(rating),
            min_rating = min(rating),
            se_rating = std(rating),
            number_of_ratings = n()) %>%
  ggplot(aes(x = Condition, y = mean_rating)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_rating + se_rating, ymax = mean_rating - se_rating)) + 
  labs(title = "Mean Rating Per Lyrics Condition",
       subtitle = "Error Bars are Standard Error of Mean",
       x = "Response Category",
       y = "Mean Rating") +
  theme_minimal() -> main_effect_lyrics)

```

* [ ] Still Need Pairs Contrast 


## GMSI Correlations


```{r}
# As Univariate 
collapsed_emotion_ratings <- df_complete %>%
  dplyr::select(subject, Happy:AngryStressful) %>%
  pivot_longer(cols = Happy:AngryStressful, names_to = "response",values_to = "rating") %>%
  group_by(subject) %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating),
            max_rating = max(rating),
            min_rating = min(rating),
            se_rating = std(rating),
            number_of_ratings = n())

df_complete %>%
  dplyr::select(subject, GENERAL, EMOTIONS) %>%
  distinct() %>%
  left_join(collapsed_emotion_ratings, by = "subject") %>%
  ggplot(aes(x = GENERAL, y = mean_rating)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(title =  "Average Rating by General Scale",
       x = "GMSI General Score",
       y = "Mean Rating") +
  theme_minimal()

df_complete %>%
  dplyr::select(subject, GENERAL, EMOTIONS) %>%
  distinct() %>%
  left_join(collapsed_emotion_ratings, by = "subject") %>%
  ggplot(aes(x = EMOTIONS, y = mean_rating)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(title =  "Average Rating by Emotion Scale",
       x = "GMSI Emotion Score",
       y = "Mean Rating") +
  theme_minimal()

```

Don't know if it is good here to use ratings of four conditions as predictor of either of these. 
Better to incorporate into a bigger model and account for individual differences in musical training in the context of everything else.



```{r}
df_complete %>%
  dplyr::select(subject, GENERAL, EMOTIONS) %>%
  distinct() %>%
  left_join(collapsed_emotion_ratings, by = "subject") %>%
  dplyr::select(mean_rating, GENERAL) %>%
  cor(use = "complete.obs")


df_complete %>%
  dplyr::select(subject, GENERAL, EMOTIONS) %>%
  distinct() %>%
  left_join(collapsed_emotion_ratings, by = "subject") %>%
  dplyr::select(mean_rating, EMOTIONS) %>%
  cor(use = "complete.obs")
```


## Include Musicality in Mixed Effects

Can also add in information at the level of song !
Also need to include familiarity with subject ! 

```{r}
library(lme4)

long_with_gmsi <- long_df_complete %>%
  left_join(df_complete %>%
              dplyr::select(subject, GENERAL, EMOTIONS))


model_a <- lmer(rating ~ Condition:response + (1 | title), data = long_df_complete)
summary(model_a)
0.04 / (0.04 + 6.96)
# Shows that variation is NOT found in grouping variable of song 
plot(model_a)
qqnorm(resid(model_a))
qqline(resid(model_a))  # pNot Good 
# Really treating likert data like ratio and that isn't the best choice

model_b <- lmer(rating ~ Condition:response + (1|title) + (1|subject), data = long_df_complete)
summary(model_b)
(.369 + .041)/(.369 + .041 + 6.621) # Variance of subject and song 

# Wont Converge If Add More random effects 


```

```{r}

# Visualise random effects 
(re.effects <- plot_model(model_b, type = "re", show.values = TRUE, title = "Fixed Effects"))

summary(model_b)

plot_model(model_b, show.values = TRUE, title = "Fixed Effects of Multi-Level Linear Model") +
  theme_minimal() -> multi_level_plot



factorial_plot  + multi_level_plot

```

* https://learningstatisticswithr.com/book/anova2.html


